\thispagestyle{plain}
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
E-commerce is the entire cycle and business activities that involve organizations or individuals conducting commercial activities using electronic means and digital information processing technology, including production, distribution, marketing, buying - selling, delivery of goods and services by electronic means.
\par
Due to these requirements, this project focuses on building and developing an e-commerce website to meet the demands of e-commerce systems in Vietnam. An e-commerce website is a website that helps users and suppliers, distributors and goods managers manage the activities of a store or a medium and small store system. For customers, the website also provides with search functions, the information of products, the information of addresses and sellers, allowing buyers to order online via various methods: transaction via Ngan Luong (an online payment website), COD order and transaction via ATM. For managers interacting with the website at levels of user, they can add, edit and delete their products according to the rights assigned by the administrator. They can also manage orders or view their store's sales in charts.
\par
There by, my topic is divided into the following sections:
\begin{itemize}
\item   CHAPTER 1: Overview of the topic.\par
In this chapter, I mentioned the main sections: Reason for choosing the topic, the target of the topic, the methods used in the project and the conclusion.
\item   Chapter 2: Theoretical basis.\par
In order to build a system of an e-commerce website, I will present several theoretical bases as a foundation to meet the proposed technical requirements such as:
\begin{itemize}
\item  Back-end: ASP.NET Core, Entity Framework Core, Identity Framework Core.
\item  Front-end: HTML (HyperText Markup Language), CSS (Cascading Style Sheets), Bootstrap, JS (Java Script), and Jquery.
\end{itemize}
\item	Chapter 3: Analysis and system design.
This chapter provides the analysis of requirements and detailed design for the e-commerce website.
\item	Chapter 4: Deployment, testing and results.
After mentioning the design analysis in chapter 3, I proceeded to perform installation testing of the proposed functions. The results of software test deployment are also mentioned.
\end{itemize}

